SMT-COMP 20243\\ 19th International Satisfiability Modulo Theory Competition

### 2024-07-20 2024/slides/presresults/slides.tex
Updated slides for 2024.

    Goals:
    \begin{itemize}
      \item spur development of SMT solver implementations
      \item promote SMT solvers and their usage
      \item support the SMT-LIB project
      \begin{itemize}
        \item to promote and develop the SMT-LIB format
        \begin{itemize}
          \item model validation
          \item proof checking
        \end{itemize}
        \item to collect relevant benchmarks
      \end{itemize}
      \item engage and include new members
    \end{itemize}
    \end{column}
    \begin{column}{0.4\textwidth}
    \begin{block}{History}
      \begin{tabular}{rp{3cm}}
        \textbf{2005} & first competition \\
        \textbf{2013} & evaluation instead \\
        & of competition\\
        \textbf{2014} & since then hosted\\
        & by \emph{StarExec}\\
        \textbf{2024} & since then hosted\\
        & by \emph{BenchExec} and the \emph{SoSy-Lab} 
      \end{tabular}
    \end{block}
    \end{column}
  \end{columns}

@@

\begin{frame}[fragile]
  \frametitle{Plans for SMT-COMP 2025?}
  \begin{itemize}
    \item General: Documentation and streamlining
    \item General: More CI support for submissions
    \item Cloud/Parallel: Integrate them into the normal process
    \item MV: Algebraic number $\implies$ non experimental
\begin{verbatim}
(root-of-with-ordering (coeffs p_0 p_1 ... p_n) i)

(root-of-with-interval  (coeffs p_0 p_1 ... p_n) min max)
(root-of-with-enclosure (coeffs p_0 p_1 ... p_n) min max)
\end{verbatim}
    Thanks for the solvers that implemented one of them!
    \item MV: partial function more discussion needed
    \item MV: array theory more discussion needed
  \end{itemize}
\end{frame}

\begin{frame}{Plans for SMT-COMP 2025?}
  \begin{itemize}
    \item Proof \textit{validation} track
      \begin{itemize}
        \item We have to analyze the data still (830gb)
        \item Ideas to turn this into a competition are welcome
      \end{itemize}

  \end{itemize}

>>>>

    Goals:
    \begin{itemize}
      \item spur development of SMT solver implementations
      \item promote SMT solvers and their usage
      \item support the SMT-LIB project
      \begin{itemize}
        \item to promote and develop the SMT-LIB format
        \begin{itemize}
          \item model validation
          \item proof checking
        \end{itemize}
        \item to collect relevant benchmarks
      \end{itemize}
      \item engage and include new members
    \end{itemize}
    \end{column}
    \begin{column}{0.4\textwidth}
    \begin{block}{History}
      \begin{tabular}{rp{3cm}}
        \textbf{2005} & first competition \\
        \textbf{2013} & evaluation instead \\
        & of competition\\
        \textbf{2014} & since then until 2024\\
        & hosted by \emph{StarExec}\\
        \textbf{2024} & since then hosted\\
        & by \emph{BenchExec} and the \emph{SoSy-Lab} 
      \end{tabular}
    \end{block}
    \end{column}
  \end{columns}

@@

\begin{frame}[fragile]
  \frametitle{Plans for SMT-COMP 2025?}
  \begin{itemize}
    \item<1-> General: documentation and streamlining
    \item<2-> General: more CI support for submissions
    \item<3-> Cloud/Parallel: (re)gain more control
      \begin{itemize}
        \item<4-> long term guarantee that the tracks will be held
        \item<5-> more transparency
        \item<6-> better communication
      \end{itemize}
    \item<7-> Proof \textit{validation} track:
      \begin{itemize}
        \item<8-> we still have to analyze the data (830gb)
        \item<9-> ideas to turn this into a competition are welcome
      \end{itemize}
    \item<10-> Derived tools: how to determine their contribution compared to the tools they are derived from
      \begin{itemize}
        \item<11-> esp. competition wide scoring, e.g., biggest contribution
        \item<12-> potential solution: run the tools they are derived from non-competitively and disqualify from logics if there is not a sufficient amount of improvement
      \end{itemize}
  \end{itemize}
\end{frame}

%\begin{frame}{Plans for SMT-COMP 2025?}
%  \begin{itemize}
%    
%
%  \end{itemize}
%
%
%\end{frame}
